\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-23 paper.tex
completed draft of id-foo classification

The remainder of this paper proceeds as follows: section \ref{classification}
takes a look at ID algorithms and classifies them. Section \ref{pattern} looks
for patterns in the implementation of these classes of algorithms, details some
of the ideas behind FCF and identifies the different aspects of the problem
space. Section \ref{design} describes the design we applied to construct the
framework, its domain specific language (DSL) and code generator. Section
\ref{evaluation} evaluates an implementation and application of the framework.
Section \ref{related} explores related work in the field of DSLs for ID and
code generation for the IoT. Finally, section \ref{conclusion} summarizes our
findings, draws conclusions and identifies topics for future work.

>>>>

The remainder of this paper proceeds as follows: section \ref{positioning}
positions our approach as a development strategy for wireless devices, section
\ref{classification} takes a look at ID algorithms and classifies them. Section
\ref{pattern} looks for patterns in the implementation of these classes of
algorithms, details some of the ideas behind FCF and identifies the different
aspects of the problem space. Section \ref{design} describes the design we
applied to construct the framework, its domain specific language (DSL) and code
generator. Section \ref{evaluation} evaluates an implementation and application
of the framework. Section \ref{related} explores related work in the field of
DSLs for ID and code generation for the IoT. Finally, section \ref{conclusion}
summarizes our findings, draws conclusions and identifies topics for future
work.

\section{\NAME as a Development Strategy}
\label{positioning}

Figure \ref{fig:approach} shows a classification of several development
strategies that can be adopted for projects involving wireless devices.

\newcommand{\ball}[5][above,yshift=+5pt]{
\tdplottransformmainscreen{#2}{#3}{#4}
\shadedraw[tdplot_screen_coords, ball color=lightgray,draw=lightgray,shading angle=-90]
  (\tdplotresx,\tdplotresy) circle (0.20)
  node[text=gray,font=\footnotesize,#1]{#5};
}

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\tdplotsetmaincoords{110}{-10}
\begin{tikzpicture}[scale=1,tdplot_main_coords]
  % axis
  \draw[very thick,->] (0,0,0) -- (7,0,0) node[anchor=north east,xshift=10mm]{$flexibility$};
  \draw[very thick,->] (0,0,0) -- (0,7,0) node[anchor=north west]{$update cost$};
  \draw[very thick,->] (0,0,0) -- (0,0,4) node[anchor=south]{$development$};
  % points
  \coordinate (O)        at (0,0,0);
  \coordinate (ideal)    at (6,0,0);
  \coordinate (vm)       at (2,2,2);
  \coordinate (modular)  at (4,4,4);
  \coordinate (reconfig) at (4,2,4);
  \coordinate (full)     at (6,6,4);
  \coordinate (cg)       at (6,4,2.5);
  % "lines"
  \draw[dashed] (2,0,0)    -- (2,2,0) -- (0,2,0);
  \draw[dashed] (4,0,0)    -- (4,4,0) -- (0,4,0);
  \draw[dashed] (6,0,0)    -- (6,6,0) -- (0,6,0);
  \draw[dashed] (vm)       -- (2,2,0);
  \draw[dashed] (modular)  -- (4,4,0);
  \draw[dashed] (full)     -- (6,6,0);
  \draw[dashed] (reconfig) -- (4,2,0);
  \draw[dashed] (cg)       -- (6,4,0);
  % "balls"
  \ball{6}{0}{0}{ideal}
  \ball{2}{2}{2}{virtual machine}
  \ball[left,xshift=-5pt]{4}{4}{4}{\shortstack{modular\\native image}}
  \ball{4}{2}{4}{\shortstack{reconfigurable\\virtual machine}}
  \ball[right,xshift=+5pt,yshift=+5pt]{6}{6}{4}{full native image}
  %\ball[right,xshift=+5pt,text=black]{6}{4.5}{3}{code generation};
  % 5. cg
  \tdplottransformmainscreen{6}{4}{2.5}
  \shadedraw[tdplot_screen_coords, ball color=gray,draw=black]
    (\tdplotresx,\tdplotresy) circle (0.20)
    node[right,xshift=+5pt,text=black,align=center,font=\footnotesize]{code generation\\+ functional code fusion};
\end{tikzpicture}
}
\caption{Classification of Development Strategies for Wireless Devices (based on \cite{sadilek2007energy})}
\label{fig:approach}
\end{figure}

Three properties are used to classify the strategies\cite{sadilek2007energy}:
flexibility, update cost and development effort. The flexibility is a measure
for the number of applications that can be deployed on a device without
physical access. The update cost is the energy required to deploy a new version
of an application on a node. The development effort covers the time to write,
test and deploy an application. The \emph{ideal} situation is that were one
ends up with a maximal flexibility and no update nor development cost.

If we consider the trade off between flexibility and update cost, we can
distinguish two extremes: virtual machines and full native images. Virtual
machines allow for very small updates due to their concise byte code, but at
the same time are restricted by the limitations of their instruction set and
predefined capabilities. A full native image on the other hand has unlimited
flexibility, but requires a large transfer of the image over the network.

Two intermediate alternatives are possible: modular native image and
reconfigurable virtual machines. With modular native images, only modules are
changed, limiting the update size, but the framework to support it is static
and limits the possibilities. Reconfigurable virtual machines take this same
approach, but apply it to virtual machines, allowing to \emph{upgrade} the
instruction set of the virtual machine.

Choosing a development strategy, with this trade off take into account, will
also determine the development cost. Developing for a virtual machine will be
less demanding than targeting a native image.

With \NAME we opt to start from the full native image, allowing full
flexibility, but try to reduce both the update cost and the development cost.
Firstly, by applying code generation and functional code fusion, we optimize
the code organisation, which has a positive effect on the code size and hence
also on the update cost. Secondly, by enabling reuse on a functional level and
automating the writing phase, the development cost is also lowered.
